Reinforcement Learning Report

### 2022-07-13 report/rl_qf_report.tex
modify policy model

\subsection{Policy Iteration}
By iteratively applying policy evaluation and policy improvement, we can obtain
a sequence of monotonically improving policies and value functions:
\[\pi_0 \overset{E}{\longrightarrow} v_{\pi_0} \overset{I}{\longrightarrow}
\pi_1 \overset{E}{\longrightarrow} v_{\pi_1} \overset{I}{\longrightarrow}
\dots \overset{I}{\longrightarrow} \pi_* \overset{E}{\longrightarrow} v_*\]
where \(\overset{E}{\longrightarrow}\) denotes a policy evaluation and
\(\overset{I}{\longrightarrow}\) denotes a policy improvement. This way of 
finding an optimal policy is called policy iteration.
\subsection{Value Iteration}
One drawback to policy iteration is that each of its iterations involves policy
evaluation, which itself is a protracted iterative computation requiring 
multiple sweeps through the state set.
\vspace{3mm}\newline We now truncate the policy evaluation such that it is
stopped after just one sweep (one update of each state):
\begin{align*}
    v_{k+1}(s)&=\underset{a}{\text{max}}\:q(s, a)\\
              &=\underset{a}{\text{max}}\:\mathbb{E}\left[
          R_{t+1}+\gamma v_k(S_{t+1})\;\middle|\;S_t=s, A_t=a\right]
\end{align*}
We keep iterate until \(v\) converges (to \(v_*\)), then we record the last
policy \(\pi(s) = \underset{a}{\text{argmax}}\:q(s, a)\).

@@

\section{Build the model}
With the environment well built, we now build the model for our policy and the
value function. In this project we use artificial neuro networks (ANNs) as the 
parameterized policy and value function, each with four linear layers, and 
with the ReLU function as the activation function. And the input of both 
function is the state, as illustrated below:
\[S_t\rightarrow\underset{\text{ANN for value function}}{
        \boxed{
            \underset{len(S)\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{256\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 1}{\text{Linear}}
        }
}\rightarrow v_t\]
\[S_t\rightarrow\underset{\text{ANN for policy function}}{
        \boxed{
            \underset{len(S)\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{256\rightarrow 512}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow n(A)}{\text{Linear}}
        }
}\rightarrow \text{Softmax}\rightarrow c_t\]
where \(len(S)\) denotes the vector length of the state and \(n(A)\) denotes the number of actions.

>>>>

\subsection{Policy Iteration}
By iteratively applying policy evaluation and policy improvement, we can obtain
a sequence of monotonically improving policies and value functions:
\[\pi_0 \overset{E}{\longrightarrow} v_{\pi_0} \overset{I}{\longrightarrow}
\pi_1 \overset{E}{\longrightarrow} v_{\pi_1} \overset{I}{\longrightarrow}
\dots \overset{I}{\longrightarrow} \pi_* \overset{E}{\longrightarrow} v_*\]
where \(\overset{E}{\longrightarrow}\) denotes a policy evaluation and
\(\overset{I}{\longrightarrow}\) denotes a policy improvement. This way of 
finding an optimal policy is called policy iteration.

\subsection{Value Iteration}
One drawback to policy iteration is that each of its iterations involves policy
evaluation, which itself is a protracted iterative computation requiring 
multiple sweeps through the state set.
\vspace{3mm}\newline We now truncate the policy evaluation such that it is
stopped after just one sweep (one update of each state):
\begin{align*}
    v_{k+1}(s)&=\underset{a}{\text{max}}\:q(s, a)\\
              &=\underset{a}{\text{max}}\:\mathbb{E}\left[
          R_{t+1}+\gamma v_k(S_{t+1})\;\middle|\;S_t=s, A_t=a\right]
\end{align*}
We keep iterate until \(v\) converges (to \(v_*\)), then we record the last
policy \(\pi(s) = \underset{a}{\text{argmax}}\:q(s, a)\).

@@

\section{Build the model}
With the environment well built, we now build the model for our policy and the
value function. In this project we use artificial neuro networks (ANNs) as the 
parameterized policy and value function, each with four linear layers, and 
with the ReLU function as the activation function. And the input of both 
function is the state, as illustrated below:
\[S_t\rightarrow\underset{\text{ANN for value function}}{
        \boxed{
            \underset{n(S)\rightarrow 64}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{64\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 64}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{64\rightarrow 1}{\text{Linear}}
        }
}\rightarrow v_t\]
\[S_t\rightarrow\underset{\text{ANN for policy function}}{
        \boxed{
            \underset{n(S)\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{256\rightarrow 512}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow n(A)}{\text{Linear}}
        }
}\rightarrow \text{Log} \rightarrow \text{Softmax}\rightarrow c_t\]
where \(n(S)\) denotes the vector length of the state and \(n(A)\) denotes 
the number of actions. 
\vspace{3mm}\newline Note that we add a log layer before the Softmax layer 
when getting the price, which takes the log of all entries of the input vector.
This shrinks the difference between those entries, so that the output of 
Softmax layer would be flatter, which means we will have a flatter policy 
distribution, which is beneficial for training since it increase the 
exploration for different actions.
